\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2022-01-31 manuscript.Rmd
x and y lab updated

F1.tic <- ggplot(F1.test.data, aes(x=Theta, y=F1.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F1: Wearing blue light filters")+geom_area()+theme(legend.position = "none")+
  aes(fill =  "#E64B3599")+
     scale_fill_identity()

F2.tic <- ggplot(F2.test.data, aes(x=Theta, y=F2.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F2: Spending time outdoors")+ylim(0,8)+
  geom_area()+aes(fill =  "#4DBBD599")+theme(legend.position = "none")+
     scale_fill_identity()

F3.tic <- ggplot(F3.test.data, aes(x=Theta, y=F3.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F3: Using phone and smart-watch in bed")+ylim(0,8)+
  geom_area()+aes(fill =  "#00A08799")+theme(legend.position = "none")+
     scale_fill_identity()

F4.tic <- ggplot(F4.test.data, aes(x=Theta, y=F4.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F4: Using light before bedtime")+
  geom_area()+aes(fill =  "#3C548899")+theme(legend.position = "none")+
     scale_fill_identity()

F5.tic <- ggplot(F5.test.data, aes(x=Theta, y=F5.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F5:Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill =  "#B09C8599")+theme(legend.position = "none")+
scale_fill_identity()

>>>>

F1.tic <- ggplot(F1.test.data, aes(x=Theta, y=F1.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F1: Wearing blue light filters")+geom_area()+theme(legend.position = "none")+
  aes(fill =  "#E64B3599")+
     scale_fill_identity()+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

F2.tic <- ggplot(F2.test.data, aes(x=Theta, y=F2.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F2: Spending time outdoors")+ylim(0,8)+
  geom_area()+aes(fill =  "#4DBBD599")+theme(legend.position = "none")+
     scale_fill_identity()+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

F3.tic <- ggplot(F3.test.data, aes(x=Theta, y=F3.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F3: Using phone and smart-watch in bed")+ylim(0,8)+
  geom_area()+aes(fill =  "#00A08799")+theme(legend.position = "none")+
     scale_fill_identity()+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

F4.tic <- ggplot(F4.test.data, aes(x=Theta, y=F4.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F4: Using light before bedtime")+
  geom_area()+aes(fill =  "#3C548899")+theme(legend.position = "none")+
     scale_fill_identity()+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

F5.tic <- ggplot(F5.test.data, aes(x=Theta, y=F5.T1)) +
  geom_line()+apatheme+
  labs(y="Test Information", title = "F5:Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill =  "#B09C8599")+theme(legend.position = "none")+
scale_fill_identity()+xlab(expression(theta)) + 
  ylab(expression(I(theta)))
